Refinements for open pNets

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
nop
Example comments

The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer. On the left, the controller component designed to be connected in the hole $\symb{ctl}$.  Its role is to decide the duration before switching the lights. 
We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third. On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$. It measures elapsed model time in ticks by counting ticks until the time limit retrieved beforehand is reached, then emits an over action with the elapsed time and restart.

In Figure \ref{fig:tlf} we present the composition of the three automata. Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.

>>>>

The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer. On the left, the controller component designed to be connected in the hole $\symb{ctl}$.  Its role is to decide the duration before switching the lights. 
We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third. On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.

In Figure \ref{fig:tlf} we present the composition of the three automata. Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component. The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer. Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter. For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both 
\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}. \\ However, the joint composition of  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and 
\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable, i.e., \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}}.
